From physical principles to ???

### 2016-02-16 2015CompleteDerivation/completeDerivation.tex
Fix typo

For discrete state variables, the total number of states is the product of the possibilities of each independent state variable. That is: if $\Delta q^1$ and $Delta q^2$ are range of possibilities for two independent variables, the total number of possibilities $\#(\Delta q^1) \#(\Delta q^2)$. These relationships are maintained during evolution by the transported variables. Since the value remains unchanged, the range of possibilities for each value remain the same: $\#(\Delta \hat{q}^i) = \#(\Delta q^i)$. The variables remain independent as well, all possible combination remain, and we have: $\#(\Delta \hat{q}^1) \#(\Delta \hat{q}^2) = \#(\Delta q^1) \#(\Delta q^2)$. These relationship will later be extended in the continuous case to independent degrees of freedom for a Hamiltonian system, and will justify the symplectic form. Though this can't be done in general and requires further assumptions.

>>>>

For discrete state variables, the total number of states is the product of the possibilities of each independent state variable. That is: if $\Delta q^1$ and $\Delta q^2$ are range of possibilities for two independent variables, the total number of possibilities $\#(\Delta q^1) \#(\Delta q^2)$. These relationships are maintained during evolution by the transported variables. Since the value remains unchanged, the range of possibilities for each value remain the same: $\#(\Delta \hat{q}^i) = \#(\Delta q^i)$. The variables remain independent as well, all possible combination remain, and we have: $\#(\Delta \hat{q}^1) \#(\Delta \hat{q}^2) = \#(\Delta q^1) \#(\Delta q^2)$. These relationship will later be extended in the continuous case to independent degrees of freedom for a Hamiltonian system, and will justify the symplectic form. Though this can't be done in general and requires further assumptions.
